\section*{Preface}
In the contemporary digital age, the security of sensitive data has become a critical concern due to the increasing volume of data exchanged across interconnected systems and the internet. This document explores key concepts surrounding data privacy attacks, cryptographic techniques, and data protection measures. The rise of cyberattacks and the constant evolution of security threats emphasize the need for robust data protection strategies to safeguard personal and organizational information. By focusing on data privacy breaches and cryptographic solutions, this work aims to provide an in-depth understanding of how attacks are executed and what countermeasures can be employed to secure systems. It also covers modern cryptographic techniques such as symmetric and asymmetric algorithms, hash functions, and public-key infrastructure (PKI), which play a vital role in protecting information integrity, confidentiality, and availability. This study is designed to guide students, researchers, and professionals in understanding and mitigating privacy risks and strengthening data security.

\newpage
\section*{Acknowledgements}
We would like to express our deepest gratitude to our professors and mentors at Atma Ram Sanatan Dharma College, Delhi University, for their continuous support, insightful feedback, and encouragement throughout the course of this research. Their guidance in both theoretical and practical aspects of cryptography and data protection has been invaluable. Special thanks to our mentor for providing critical feedback that helped shape our approach to understanding data privacy attacks and cryptographic defenses. We are also thankful for the resources and tools provided by ARSD College, which were instrumental in the successful completion of this work. We would like to extend our appreciation to the authors and researchers whose works have been referenced in this document, especially William Stallings' \textit{Information Privacy Engineering and Privacy by Design}, which provided a comprehensive foundation for understanding privacy threats and regulations. Finally, we acknowledge the contributions of our peers, whose discussions and input have enhanced the quality of this study.


\newpage
\section*{About the Authors}
\subsection*{Sudeep Kumar Singh}
Sudeep Kumar Singh is a third-year student of B.Sc. Computer Science (Hons.) at Atma Ram Sanatan Dharma College, Delhi University. 

\subsection*{Shubham Kushwaha}
Shubham Kushwaha is also a third-year student pursuing B.Sc. Computer Science (Hons.) at Atma Ram Sanatan Dharma College, Delhi University. 

\subsection*{Ankit Sarawag}
Ankit Sarawag, is also a third-year student pursuing B.Sc. Computer Science (Hons.) at Atma Ram Sanatan Dharma College, Delhi University. 

\newpage
\section*{Credits}
\begin{itemize}
    \item \textbf{Sudeep Kumar Singh (28021), Shubham Kushwaha (28090), and Ankit Sarawag (28006)}, students of B.Sc. Computer Science (Hons.) at Atma Ram Sanatan Dharma College, Delhi University, have collaborated on this project.
    
    \item The concepts and theories discussed in this work are based on the book:  
    \textbf{Stallings, William.} \textit{Information Privacy Engineering and Privacy by Design: Understanding Privacy Threats, Technology, and Regulations Based on Standards and Best Practices}. Addison-Wesley Professional, 2019.
\end{itemize}


