% Chapter Title Page
\clearpage
\thispagestyle{empty} 
\begin{center}
    \vspace*{\fill} 
    \Huge \textbf{Chapter 2} \\
    \Huge \textbf{Security Services} 
    \vspace*{\fill}
\end{center}
\clearpage

\chapter{Security Services}

A security service supports security requirements such as confidentiality, integrity, availability, authenticity, and accountability.\index{Security Service}\phantomsection\label{SecurityService}. These services implement security policies using security mechanisms.\index{Security Mechanism}\phantomsection\label{SecurityMechanism}

\section{Key Security Services}
\begin{table}[h!]
    \centering
    \caption{Key Security Services}
    \vspace{0.4cm}
\begin{tabular}{|p{3.5cm}|p{9cm}|}
    \hline
    \textbf{Service} & \textbf{Description} \\ \hline
    \textbf{Authentication} & Determines a person’s identity before granting access.\index{Authentication}\phantomsection\label{Authentication} \\ \hline
    \textbf{Access Control} & Limits or allows access to resources for specific purposes.\index{Access Control}\phantomsection\label{AccessControl} \\ \hline
    \textbf{Data Confidentiality} & Ensures information is only available to intended persons.\index{Data Confidentiality}\phantomsection\label{DataConfidentiality} \\ \hline
    \textbf{Data Integrity} & Ensures information is modified only by authorized persons and in appropriate ways.\index{Data Integrity}\phantomsection\label{DataIntegrity} \\ \hline
    \textbf{Nonrepudiation} & Prevents a person from denying an action they performed.\index{Nonrepudiation}\phantomsection\label{Nonrepudiation} \\ \hline
    \textbf{Availability} & Ensures apps, services, and hardware are ready and perform acceptably when needed.\index{Availability}\phantomsection\label{Availability} \\ \hline
\end{tabular}
\end{table}

\section{Authentication}
\begin{itemize}
    \item \textbf{Purpose:} Ensures communication is authentic.\index{Authentication!Purpose}\phantomsection\label{AuthenticationPurpose}
    \begin{itemize}
        \item \textbf{Single Message:} Ensures the recipient that the message is from the claimed source.\index{Authentication!Single Message}\phantomsection\label{SingleMessage}
        \item \textbf{Ongoing Interaction:} Ensures both entities are authentic and the connection is not interfered with.\index{Authentication!Ongoing Interaction}\phantomsection\label{OngoingInteraction}
    \end{itemize}
    \item \textbf{Types of Authentication:}
    \begin{itemize}
        \item \textbf{Peer Entity Authentication:} Confirms the identity of a peer entity in an association, preventing masquerade or unauthorized replay.\index{Peer Entity Authentication}\phantomsection\label{PeerEntityAuthentication}
        \item \textbf{Data Origin Authentication:} Corroborates the source of a data unit, supporting applications like email.\index{Data Origin Authentication}\phantomsection\label{DataOriginAuthentication}
    \end{itemize}
\end{itemize}

\section{Access Control}
\begin{itemize}
    \item \textbf{Purpose:} Limits and controls access to systems and applications via communications links.\index{Access Control!Purpose}\phantomsection\label{AccessControlPurpose}
    \item \textbf{Requirement:} Identification or authentication of each entity to tailor access rights.\index{Access Control!Requirement}\phantomsection\label{AccessControlRequirement}
\end{itemize}

\section{Data Confidentiality}
\begin{itemize}
    \item \textbf{Purpose:} Protects transmitted data from passive attacks.\index{Data Confidentiality!Purpose}\phantomsection\label{DataConfidentialityPurpose}
    \item \textbf{Protection Levels:}
    \begin{itemize}
        \item Protection of all user data over a connection.\index{Data Confidentiality!User Data Protection}\phantomsection\label{UserDataProtection}
        \item Protection against traffic flow analysis.\index{Data Confidentiality!Traffic Flow Analysis}\phantomsection\label{TrafficFlowAnalysis}
    \end{itemize}
    \item \textbf{Requirement:} Prevents attackers from observing source, destination, frequency, length, or other characteristics of communication.\index{Data Confidentiality!Requirement}\phantomsection\label{DataConfidentialityRequirement}
\end{itemize}

\section{Data Integrity}
\begin{itemize}
    \item \textbf{Purpose:} Ensures messages are received as sent, without modification.\index{Data Integrity!Purpose}\phantomsection\label{DataIntegrityPurpose}
    \item \textbf{Types of Integrity Service:}
    \begin{itemize}
        \item \textbf{Connection-Oriented Integrity:} Addresses message stream modification and denial of service for streams of messages.\index{Connection-Oriented Integrity}\phantomsection\label{ConnectionOrientedIntegrity}
        \item \textbf{Connectionless Integrity:} Provides protection against individual message modification.\index{Connectionless Integrity}\phantomsection\label{ConnectionlessIntegrity}
    \end{itemize}
\end{itemize}

\section{Nonrepudiation}
\begin{itemize}
    \item \textbf{Purpose:} Prevents sender or receiver from denying transmitted messages.\index{Nonrepudiation!Purpose}\phantomsection\label{NonrepudiationPurpose}
    \begin{itemize}
        \item \textbf{Sender Nonrepudiation:} Receiver can prove the sender sent the message.\index{Sender Nonrepudiation}\phantomsection\label{SenderNonrepudiation}
        \item \textbf{Receiver Nonrepudiation:} Sender can prove the receiver received the message.\index{Receiver Nonrepudiation}\phantomsection\label{ReceiverNonrepudiation}
    \end{itemize}
\end{itemize}

\section{Availability Service}
\begin{itemize}
    \item \textbf{Purpose:} Ensures system or resource is accessible and usable on demand.\index{Availability!Purpose}\phantomsection\label{AvailabilityPurpose}
    \item \textbf{Requirement:} System provides services as designed whenever users request them.\index{Availability!Requirement}\phantomsection\label{AvailabilityRequirement}
    \item \textbf{Protection:} Addresses security concerns raised by denial-of-service attacks, depending on access control and other security services.\index{Denial of Service}\phantomsection\label{DenialOfService}\index{Availability!Protection}\phantomsection\label{AvailabilityProtection}
\end{itemize}

\section{Conclusion}
These security services are essential for maintaining a secure data processing and communication environment in organizations.
