\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc} % Encoding
\usepackage{geometry} % For custom page dimensions
\usepackage{setspace} % For line spacing
\usepackage{fancyhdr} % For header and footer
\usepackage{hyperref} % For clickable links

% Custom page dimensions and margins
\geometry{
    a4paper,
    left=1in,
    right=1in,
    top=1in,
    bottom=1in
}

% Title, author, and date
\title{\textbf{Professional Profile of Sudeep Kumar Singh}}
\author{Sudeep Kumar Singh}
\date{\today}

% Address
\newcommand{\address}{B.Sc. Computer Science (Hons.) \\ Atma Ram Sanatan Dharma College, New Delhi, India}

% Custom header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Sudeep Kumar Singh - Profile}
\fancyhead[R]{\today}
\fancyfoot[C]{\thepage}

% Document begins
\begin{document}

\maketitle
\begin{center}
    \address \\
    \vspace{0.5cm}
    \textbf{Contact Details:} \\
    Email: \href{mailto:sudeepkumarsingh2003@gmail.com}{sudeepkumarsingh2003@gmail.com} \\
    Phone: +91 7667912716 \\
    GitHub: \href{https://github.com/sudeepwebdev}{sudeepwebdev} \\
    LinkedIn: \href{https://linkedin.com/in/sudeepwebdev}{sudeepwebdev}
\end{center}

% Adjust line spacing
\setstretch{1.5}

\section*{About Me}

Hello! My name is Sudeep Kumar Singh. I am a web and app developer currently pursuing my third year of a B.Sc. in Computer Science (Hons.) at Atma Ram Sanatan Dharma College, New Delhi. I am proficient in multiple languages and frameworks, constantly learning new technologies to expand my skill set.

\section*{Skills}

\textbf{Languages}: English, Hindi \\
\textbf{Programming Languages}: HTML, CSS, JavaScript, Python, C++, Dart, SQL, Kotlin (learning), Go, C\# \\
\textbf{Frameworks and Libraries}: Django, Node.js, Bootstrap, Flutter, Tailwind CSS \\
\textbf{Databases}: Firestore, Firebase Realtime Database, MySQL \\
\textbf{Operating Systems}: Linux, Windows \\
\textbf{Cloud-Ops (Learning)}: Firebase, Azure, Google Cloud Platform \\
\textbf{Other Skills}: Canva, Google Workspace, Microsoft 365, LaTeX

\section*{Projects}

- \textbf{Mathateria} (Website) - A learning platform for math students. \\
  Tech Stack: HTML, CSS, JavaScript, Firebase \\
  Link: \href{https://mathopedia-c702b.web.app/}{mathopedia-c702b.web.app}

- \textbf{College Timetable} (Website) - A schedule management tool for college use. \\
  Tech Stack: Flutter, Firebase \\
  Link: \href{https://timetable.arsdcollege.ac.in/}{timetable.arsdcollege.ac.in}

- \textbf{DevDocuments} (Website) - A resource platform for developers. \\
  Tech Stack: Flutter, Firebase \\
  Link: \href{https://devdocuments.web.app/}{devdocuments.web.app}

- \textbf{College Seminar Booking Portal} (Website) - A portal for booking college seminar rooms. \\
  Tech Stack: Flutter, Firebase \\
  Link: \href{https://seminar.arsdcollege.ac.in/}{seminar.arsdcollege.ac.in}

- \textbf{Rewards Assistant} (Browser Extension) - A productivity tool with over 9K users. \\
  Tech Stack: HTML, CSS, JavaScript, Edge API \\
  Link: \href{https://edge-stats.com/d/kkpjhahghfmbiibocfblallmginjfbpb}{Rewards Assistant on Edge Store}

- \textbf{Convertrix} (Website) - A unit conversion tool. \\
  Tech Stack: HTML, CSS, JavaScript, Firebase \\
  Link: \href{https://convert-rix.web.app/}{convert-rix.web.app}

- \textbf{Student Management System} (App) - A student tracking app. \\
  Tech Stack: Flutter, Firebase

\end{document}
