% Chapter Title Page
\clearpage
\thispagestyle{empty} 
\begin{center}
    \vspace*{\fill} 
    \Huge \textbf{Chapter 2} \\
    \Huge \textbf{Security Services} 
    \vspace*{\fill}
\end{center}
\clearpage

\chapter{Security Services}

A security service supports security requirements such as confidentiality, integrity, availability, authenticity, and accountability. These services implement security policies using security mechanisms.

\section{Key Security Services}
\begin{table}[h!]
    \centering
\begin{tabular}{|p{3.5cm}|p{9cm}|}
    \hline
    \textbf{Service} & \textbf{Description} \\ \hline
    \textbf{Authentication} & Determines a person’s identity before granting access. \\ \hline
    \textbf{Access Control} & Limits or allows access to resources for specific purposes. \\ \hline
\textbf{Data Confidentiality} & Ensures information is only available to intended persons.
 \\ \hline
    \textbf{Data Integrity} & Ensures information is modified only by authorized persons and in appropriate ways. \\ \hline
    \textbf{Nonrepudiation} & Prevents a person from denying an action they performed. \\ \hline
    \textbf{Availability} & Ensures apps, services, and hardware are ready and perform acceptably when needed. \\ \hline
\end{tabular}
\caption{Key Security Services}
\end{table}
\section{Authentication}
\begin{itemize}
    \item \textbf{Purpose:} Ensures communication is authentic.
    \begin{itemize}
        \item \textbf{Single Message:} Ensures the recipient that the message is from the claimed source.
        \item \textbf{Ongoing Interaction:} Ensures both entities are authentic and the connection is not interfered with.
    \end{itemize}
    \item \textbf{Types of Authentication:}
    \begin{itemize}
        \item \textbf{Peer Entity Authentication:} Confirms the identity of a peer entity in an association, preventing masquerade or unauthorized replay.
        \item \textbf{Data Origin Authentication:} Corroborates the source of a data unit, supporting applications like email.
    \end{itemize}
\end{itemize}

\section{Access Control}
\begin{itemize}
    \item \textbf{Purpose:} Limits and controls access to systems and applications via communications links.
    \item \textbf{Requirement:} Identification or authentication of each entity to tailor access rights.
\end{itemize}

\section{Data Confidentiality}
\begin{itemize}
    \item \textbf{Purpose:} Protects transmitted data from passive attacks.
    \item \textbf{Protection Levels:}
    \begin{itemize}
        \item Protection of all user data over a connection.
        \item Protection against traffic flow analysis.
    \end{itemize}
    \item \textbf{Requirement:} Prevents attackers from observing source, destination, frequency, length, or other characteristics of communication.
\end{itemize}

\section{Data Integrity}
\begin{itemize}
    \item \textbf{Purpose:} Ensures messages are received as sent, without modification.
    \item \textbf{Types of Integrity Service:}
    \begin{itemize}
        \item \textbf{Connection-Oriented Integrity:} Addresses message stream modification and denial of service for streams of messages.
        \item \textbf{Connectionless Integrity:} Provides protection against individual message modification.
    \end{itemize}
\end{itemize}

\section{Nonrepudiation}
\begin{itemize}
    \item \textbf{Purpose:} Prevents sender or receiver from denying transmitted messages.
    \begin{itemize}
        \item \textbf{Sender Nonrepudiation:} Receiver can prove the sender sent the message.
        \item \textbf{Receiver Nonrepudiation:} Sender can prove the receiver received the message.
    \end{itemize}
\end{itemize}

\section{Availability Service}
\begin{itemize}
    \item \textbf{Purpose:} Ensures system or resource is accessible and usable on demand.
    \item \textbf{Requirement:} System provides services as designed whenever users request them.
    \item \textbf{Protection:} Addresses security concerns raised by denial-of-service attacks, depending on access control and other security services.
\end{itemize}

\section{Conclusion}
These security services are essential for maintaining a secure data processing and communication environment in organizations.
